---
title: "Alcohol vs Seat choice"
author: "Maria Cabanillas"
date: "October 13, 2020 "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: there is no difference in the mean alcohol consumption based on seating location  
$H_A$: there is a difference between at least two places where people sit in average alcohol consumption

## Now with ggplot - first select the basic data
 
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

the p value is 0.000116 < 0.05 we reject the null hypothesis

```{r}
plot(TukeyHSD(model1))
```
## Conclusions

there is a difference between alcohol consumption and seating for the front-back, there is a difference between alcohol consumption and seating for middle-back, there is no difference between alcohol consumption and seating for middle-front.
